---
title: "Prediction Assignment"
author: "abdimoh"
date: "Sunday, December 21, 2014"
output: html_document
---

#                  Prediction Assignment

The data is based on Human Activity Recognition

Getting the data and cleaning it

```{r, echo=TRUE}

#exc<-read.csv("pml-training.csv", stringsAsFactors = FALSE)
exc<-read.csv("pml-training.csv")
exc<-exc[,colSums(is.na(exc))<19000]
exc<-exc[,colSums(exc != "") > 19000]
exc<-exc[,-1]


```


Partitioning and preparing training and test data

```{r, echo=TRUE}
library(caret)
library(kernlab)

inTrain<-createDataPartition(y=exc$classe, p=0.75, list=FALSE)
training<-exc[inTrain,]
testing<-exc[-inTrain,]

```

The model is buit based on random forest and then tested on the test data. I tried the principal component as preprocessing and used glm, but got better results with random forest as the confusion matrix below shows.
This model also predicted the automatic grading assignment correctly.


```{r, echo=TRUE}
library(randomForest)
modelFit<-randomForest(classe ~ ., data=training, ntree=100, importance = TRUE, prox =FALSE)
predictionrf <- predict(modelFit, testing)
confusionMatrix(testing$classe, predictionrf)
```

Finally we apply the machine learning algorithm to the 20 test cases available in the test data submitted to the automatic grading
```{r,echo=TRUE}
exctest<-read.csv("pml-testing1.csv")
exctest<-exctest[,colSums(is.na(exctest))<10]
exctest<-exctest[,colSums(exctest != "") > 10]
exctest<-exctest[,-1]

levels(exctest$cvtd_timestamp)<-levels(training$cvtd_timestamp)
levels(exctest$new_window)<-levels(training$new_window)


test1predictionrf <- predict(modelFit, exctest)

test1predictionrf

